\documentclass[a4paper]{article}
\title{\large \textbf{Crowdsourcing in Question \& Answer Systems}\\ CSIT6910A Independent Project}
\author{\small WANG Yue}
\date{\small \today}
\begin{document}
\maketitle
\centerline{\emph{Supervised by Prof. Wilfred Ng, HKUST}}
\section{Introduction}

Crowdsourcing is the practice of obtaining needed services, ideas, or content by soliciting contributions from a large group of people, and especially from an online community, rather than from traditional employees or suppliers. Nowadays, lots of people begain to post their ideas and viewpoints on SNS platforms such as Twitter, Facebook or Sina Weibo. Such information can be collected to identify what is users are good at. Analysising this data on SNS platform can help recognize which
expert the user would be on question and answer systems. In a result, the system could provide more accurate people when a user ask a question.

\section{Project Workload}
\begin{itemize}
        \item Using network spiders to crawl data from Q\&A systems: Yahoo Answers, Quora, Baidu Zhidao
        \item Get the user data from various SNS platform: Twitter, Facebook, Sina Weibo, either using spider or open platform api.
        \item Match the usr data from sns with Q\&A system to help the system use the data to improve the matching accuracy
\end{itemize}

\section{Meeting Schedule}
\begin{itemize}
        \item At least 4 meetings will be arranged throught out the semester, detailed schedules will be discussed with the professor.
        \item Minutes of each meeting will be attached in the final report
\end{itemize}
\section{Grading Criteria}
\begin{itemize}
        \item Project Proposal: 10\%
        \item Final repot: 60\%
        \item Presentation: 30\%
\end{itemize}
\end{document}
